Fuels, fire weather, and Rx fire behavior in North Dakota

### 2021-02-09 writeups/FuelsWeatherFirebehavior.Rmd
Update FuelsWeatherFirebehavior.Rmd

```{r data_prep, eval=FALSE}
 AllData <-  
    read_csv(paste0(FilePath, "data/fromMZ/CompiledData2.csv")) %>%
    filter(location != "OAK") %>%
      mutate(date = as.Date(date, format = "%m/%d/%Y"),
               L = str_remove(location, "REC"), 
               B = str_sub(block, 1,3), 
               Ps = str_replace(pasture, "[.]", ""), 
               Ps = str_sub(Ps, 1,2), 
               patch = str_replace(patch, "[.]", ""),
               y = format(date, "%y")) %>%
        unite("FireCode", c(L,B,Ps,patch,y), sep=".") %>%
    mutate(time = str_remove(MaxTempTime, "[.]+[0-9]"))%>%
    unite(timestamp, c(date, time), sep = " ") %>%
    mutate(timestamp = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S")) %>%
        select(FireCode, timestamp, plot, array, TC, MaxC, 
               AirTemp, RH, dpC, MaxWindSpeed, 
               LAI, FMC, KgHa)

>>>>

```{r data_prep, eval=FALSE}
 AllData <-  
    read_csv(paste0(FilePath, "/data/fromMZ/CompiledData2.csv")) %>%
    filter(location != "OAK") %>%
      mutate(date = as.Date(date, format = "%m/%d/%Y"),
               L = str_remove(location, "REC"), 
               B = str_sub(block, 1,3), 
               Ps = str_replace(pasture, "[.]", ""), 
               Ps = str_sub(Ps, 1,2), 
               patch = str_replace(patch, "[.]", ""),
               y = format(date, "%y")) %>%
        unite("FireCode", c(L,B,Ps,patch,y), sep=".") %>%
    mutate(time = str_remove(MaxTempTime, "[.]+[0-9]"))%>%
    unite(timestamp, c(date, time), sep = " ") %>%
    mutate(timestamp = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S")) %>%
        select(FireCode, timestamp, plot, array, TC, MaxC, 
               AirTemp, RH, dpC, MaxWindSpeed, 
               LAI, FMC, KgHa)
